Rectangulation polytopes

### 2024-03-20 draft/rectangulotopes.tex
additional statements

Two leaves of the trees $T(R)$ and $S(R)$ are said to be \defn{common leaves} if they are both either horizontal or vertical, and the edges to their parents lie on the same segment of $R$. We also denote by $i|j$ and $\frac{\ j\ }i$ the situations where the rectangle labeled $i$ touches the rectangle labeled $j$ from the left and from below in $R$, respectively.

>>>>

Two leaves of the trees $T(R)$ and $S(R)$ are said to be \defn{common leaves} if the edges to their parents lie on the same segment of $R$. We denote by $i|j$ and $\frac{\ j\ }i$ the situations where the rectangle labeled $i$ touches the rectangle labeled $j$ from the left and from below in $R$, respectively.
